---
title: "HW9_answers.Rmd"
author: "Jaimee Pyron"
date: "10/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Questions:

1. Are the data in a flat file format? 
Yes, a .csv is considered flat file format. 

2. What is the structure of the data?  Are there any variables you might need to convert prior to manipulating the data?
It is a data frame. All values are correctly labelled as numeric except country. This will need to be converted to character. This can be done
as follows:
```r
emissions$country <- as.character(emissions$country)
```

3. What countries had per capita emissions larger than the 95th percentile in 2014? Make a table of their names and per capita emissions. Hint: Use quantile() to find the 95% cutoff.

```{r, echo=FALSE}
percentile = quantile(emissions$X2014, 0.95, na.rm=TRUE)
dat <- rep("NA", 9)
table <- data.frame("cntry"=dat, "perCapEm.2014"=dat)
table$country <- gap_co2$cntry[emissions2$X2014 > 15.40000]
table$perCapEm.2014 <- gap_co2$X2014[emissions$X2014 > 15.40000]
table %>%
  kable() %>%
  kable_styling()
```
perc
4. Make a table comparing the per capita emissions of the US and the world's highest per capita emitter (from above)  in 1925, 1950, and 2014.  

```{r, echo=FALSE}
val <- emissions[emissions$country %in% c("United States", "Qatar"), ]
dat <- val[ , c("X1925", "X1950", "X2014")]
top <- data.frame(dat)
row.names(top) <- c("1925", "1950", "2014")
column.names(top) <- ("Qatar","United States") 
top %>%
  kable() %>%
  kable_styling()
```



