---
title: "HW9_Answers"
author: "Zack Grzywacz"
date: "October 29, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(markdown)
library(knitr)
library(kableExtra)
```

1. Are the data in a flat file format? 

```{r}
gap_co2 <- read.csv("./data/co2_emissions_tonnes_per_person_gapminder.csv")
```

No, this is in an excel .csv format.

2. What is the structure of the data?  Are there any variables you might need to convert prior to manipulating the data?

```{r}
str(gap_co2)
```

This data is in a dataframe. All variables are numbers except for "country", which is a factor. We will convert it to a character vector.

```{r}
gap_co2$country <- as.character(gap_co2$country)
```


3. What countries had per capita emissions larger than the 95th percentile in 2014? Make a table of their names and per capita emissions. Hint: Use quantile() to find the 95% cutoff.

```{r}
quantile(gap_co2$X2014, probs = seq(0, 1, 0.05))
```

The cutoff is 15.4

```{r}
gap_co2$country[gap_co2$X2014 > 15.40000]
```

